BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-11 tex/5-evaluation.tex
Partial fixes.

Our evaluation is articulated in two parts. First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting content and title from web articles\comment{article has a different meaning here than what we've been using in the rest of the paper. Maybe switch to "capable of extracting content from web pages"?}. The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time. Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code. Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate the article and title extraction from a blog post we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively. These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}). \autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.

@@

% running time eval, scalability with size of blogs
In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all previously published content on a blog\comment{"previously published" sounds a bit weird. Maybe something like "already published" or just "published"?}.

@@

Past the initial computations, the cost to extract an article with our approach is almost null\comment{zero, instead of null?}. This is a consequence of having a blog-aware, rule-based algorithm. If you recall\comment{a bit informal, switch to something like: "As already mentioned"?} the procedure presented in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog. In this example, the cost, in time, for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is not\comment{not --> almost not / barely} visible on the scale of \autoref{runningtime}. The three other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to close to linear running times.

>>>>

Our evaluation is articulated in two parts. First, we compare the article extraction procedure presented in \autoref{algorithms} with three open-source projects capable of extracting article and title from web pages. The comparison will show that our blog-targeted solution has better performance both in terms of success rate and running time. Second, a discussion is held regarding the different solutions available to archive data beyond what is available in the HTML source code. Extraction of authors, dates and comments is not part of this evaluation because of the lack of publicly available competing projects and reference data sets.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction success rates}
To evaluate article and title extraction from blog posts we compared our approach to three open source projects: Readability \cite{python-readability2011}, Boilerpipe \cite{kohlschuetter2010} and Goose \cite{goose2012}, implemented in JavaScript, Java and Scala respectively. These projects are more generic than our blog-specific approach in the sense that they are able to identify and extract data directly from HTML source code, and do not make use of web feeds or structural similarities between pages of the same blog (observations \ref{havefeedAssum} and \ref{similarhtmlAssum}). \autoref{precisionTable} shows the extraction success rates for article and title on a test sample of 2300 blog posts obtained from the Spinn3r dataset \cite{burton2011}.

@@

% running time eval, scalability with size of blogs
In addition to the quality of the extracted data we also evaluated the running time of the extraction procedure. The main point of interest is the ability of the extraction procedure to scale as the number of posts in the processed blog increases. This corresponds to the evaluation of a \emph{NewCrawl} task, which is in charge of harvesting all published content on a blog.

@@

Past the initial computations, the cost to extract an article with our approach is almost zero. This is a consequence of having a blog-aware, rule-based algorithm. As already mentioned in \autoref{algorithms}, the central idea is to first build extraction rules using the information provided by the web feed, and then use these rules on all posts of the blog. In this example, the cost, in time, for parsing a new blog post and applying the extraction rules is in the order of 3 milliseconds, which is barely not visible on the scale of \autoref{runningtime}. The three other evaluated solutions do not function this way: each blog post is processed as new and independent input, leading to close to linear running times.
